---
title: "Homework 2: Data visualization"
author: "your name"
date: "due 11:59pm 6/02/2020"
output: html_document
---

# Learning Objectives

1.	Write a few sentences for a journal methods section describing the data and the analysis you are going to perform  
2.	Perform 2 different dimension reduction techniques      
3. Create a figure to show the results from each dimension reduction method you performed  
4. Describe the information conveyed by the figures  


**Assignment**: You will perform at least two of the statistical analysis methods we learned in class on a new data set and interpret the results. 

Steps to follow:

1. Run the code hw2-format-data.Rmd in the class folder to download the homework data from the GEO website to an R object in your data folder.
2. QC the data in the R object provided. Are the expression data and annotation data identically sorted? Are there missing data? Patient samples are measured at how many time points?  
3. Write a brief introduction to describe the data in your analysis, and the methods you will apply for dimension reduction. Describe any other data manipulation you will perform.  
4. Perform dimension reduction technique and display the results in a figure. Describe any patterns the figure shows.  
5. Perform a different dimension reduction technique and report the results.
6. Verify that your report is reproducible or modify your code so that it is reproducible.  

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r loadlibraries}
library(bookdown)
library(matrixStats)
library(limma)
library(Rtsne)
library(ggplot2)
```


# Load the human alveolar epithelial cell dataset

These data are from Marconett et al. Integrated transcriptomic and epigenomic analysis of primary human lung cell differentiation. PLoS Genet 2013. PMC3688557. 

GEO assession: GSE38571

Data set: 17 Illumina HT12v4 arrays

2 Experimental Factors:

		5 Time points: D0, D2, D4, D6, D8	   (day)
		
		3 lung donors: 49, 61, 66		         (age) 


```{r aecdata}
   load("../data/aec.rda")
```

Summarize the data. 

```{r structure}
names(aec)
```


```{r }

```

Write a few sentences summarizing the data set here, and the methods you are going to apply to the data.

# Data Visualization

## Method 1:



```{r }


```


## Method 2:



```{r }

```



# Report computing environment

Now output the computing environment listing the different software versions installed on your computer.

```{r sessioninfo}
  sessionInfo()
```
